### 2019-05-20 2019_csic5011/project2/project2.tex
project2 added

\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{page}{1}
   \setcounter{section}{0}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf CSIC5011: Top and Geo Data Reduction \hfill #4} }
       \vspace{6mm}
       \hbox to 6.28in { {\Large \hfill #1  \hfill} }
       \vspace{6mm}
       \hbox to 6.28in { {\it Instructor: #2\hfill #3} }
      \vspace{2mm}}
   }
   \end{center}
   \markboth{#1}{#1}
   \vspace*{4mm}
}

@@

\lecture{Mini-Project 1}{Yuan Yao}{Due: 0:00am Monday 8 Apr, 2019}{20 Mar, 2019}

@@

\section{Mini-Project Requirement and Datasets}

This project as a warmup aims to exercise the tools in the class, such as PCA/MDS and their various extensions, biased estimators, etc., based on the real datasets. In the below, we list some candidate datasets for your reference.

\begin{enumerate}
\item Pick up ONE (or more if you like) favorite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to THREE persons per group, to work on the same problem. Each team just submit ONE report, \emph{with a clear remark on each person's contribution}. The report can be in the format of a \emph{technical report within 8 pages}, e.g. NIPS conference style 
\begin{center}
\url{https://nips.cc/Conferences/2016/PaperInformation/StyleFiles} \\
and a sample file at \\
\url{https://arxiv.org/pdf/1606.04930.pdf} 
\end{center}
or of a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
\item In the report, (1) design or raise your scientific problems (a good problem is sometimes more important than solving it); (2) show your main results with a careful analysis supporting the results toward answering your problems. Remember: scientific analysis and reasoning are more important than merely the performance results. Reproducible source codes may be submitted via a \url{https://github.com/} link, through email as a zip file, or as an appendix of the report if it is not large.    
\item Submit your report by email or paper version no later than the deadline, to the following address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}). 
\end{enumerate}

@@

\section{Hand-written Digits} The website

\url{http://www-stat.stanford.edu/\~tibs/ElemStatLearn/datasets/zip.digits/}

\noindent contains images of 10 handwritten digits (`$0$',...,`9');

@@

%\section{Identification of Raphael's paintings from the forgeries}
%
%The following data, provided by Prof. Yang WANG from HKUST,
%
%\url{https://drive.google.com/folderview?id=0B-yDtwSjhaSCZ2FqN3AxQ3NJNTA&usp=sharing}
%
%\noindent contains a 28 digital paintings of Raphael or forgeries. Note that there are both jpeg and tiff files, so be careful with the bit depth in digitization. The following file
%
%\url{https://docs.google.com/document/d/1tMaaSIrYwNFZZ2cEJdx1DfFscIfERd5Dp2U7K1ekjTI/edit}
%
%\noindent contains the labels of such paintings, which are 
%\begin{enumerate}
%\item[1] Maybe Raphael - Disputed
%\item[2] Raphael
%\item[3] Raphael
%\item[4] Raphael
%\item[5] Raphael
%\item[6] Raphael
%\item[7] Maybe Raphael - Disputed
%\item[8] Raphael
%\item[9] Raphael
%\item[10] Maybe Raphael - Disputed
%\item[11] Not Raphael
%\item[12] Not Raphael
%\item[13] Not Raphael
%\item[14] Not Raphael
%\item[15] Not Raphael
%\item[16] Not Raphael
%\item[17] Not Raphael
%\item[18] Not Raphael
%\item[19] Not Raphael
%\item[20] My Drawing (Raphael?)
%\item[21] Raphael
%\item[22] Raphael
%\item[23] Maybe Raphael - Disputed
%\item[24] Raphael
%\item[25] Maybe Raphael - Disputed
%\item[26] Maybe Raphael - Disputed
%\item[27] Raphael
%\item[28] Raphael
%\end{enumerate}
%Can you exploit the known Raphael vs. Not Raphael data to predict the identity of those 6 disputed paintings (maybe Raphael)? The following student poster report seems a good exploration
%
%\url{http://math.stanford.edu/~yuany/course/2015.fall/poster/Raphael_LI\%2CYue_1300010601.pdf}
%
%The following paper by Haixia Liu, Raymond Chan, and me studies Van Gogh's paintings which might be a reference for you:
%
%\url{http://dx.doi.org/10.1016/j.acha.2015.11.005}

@@

\section*{Peer Review}

Deadline is 11:59pm April 16, 2019. Submit your review in plain text to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Review}. Rebuttal is open afterwards.

\begin{itemize}
\item Summary of the report.
\item Describe the strengths of the report. 
\item Describe the weaknesses of the report.
\item Evaluation on Clarity and quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
\item Evaluation on Technical Quality (1-5): Are the results technically sound? Are there obvious flaws in the reasoning? Are claims well-supported by theoretical analysis or experimental results? Are the experiments well thought out and convincing? Will it be possible for other researchers to replicate these results? Is the evaluation appropriate? Did the authors clearly assess both the strengths and weaknesses of their approach? Are relevant papers cited, discussed, and compared to the presented work?
\item Overall rating: (5- My vote as the best-report. 4- A good report. 3- An average one. 2- below average. 1- a poorly written one). 
\item Confidence on your assessment (1-3)
(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
\end{itemize}

\section*{Rebuttal}
The rebuttal period starts from now, till 11:59pm April 21, 2019. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or word DOC format to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.

>>>>

\newcommand{\lecture}[4]{
   \pagestyle{myheadings}
   \thispagestyle{plain}
   \newpage
   \setcounter{page}{1}
   \setcounter{section}{0}
   \noindent
   \begin{center}
   \framebox{
      \vbox{\vspace{2mm}
    \hbox to 6.28in { {\bf Topological and Geometric Data Reduction \hfill #4} }
       \vspace{6mm}
       \hbox to 6.28in { {\Large \hfill #1  \hfill} }
       \vspace{6mm}
       \hbox to 6.28in { {\it Instructor: #2\hfill #3} }
      \vspace{2mm}}
   }
   \end{center}
   \markboth{#1}{#1}
   \vspace*{4mm}
}

@@

\lecture{Final Project}{Yuan Yao}{Due: 23:59 Sunday 19 May, 2019}{3 May, 2019}

@@

\section{Project Requirement and Datasets}

In the below, we list some candidate datasets for your reference. You are also encouraged to work on your own datasets in the final project, upon the approval of the instructor.

\begin{enumerate}
\item Pick up ONE (or more if you like) favourite dataset below to work. If you would like to work on a different problem outside the candidates we proposed, please email course instructor about your proposal.  
\item Team work: we encourage you to form small team, up to THREE persons per group, to work on the same problem. Each team must submit:
\subitem(a) \emph{ONE report}, \emph{with a clear remark on each person's contribution}. The report can be in the format of a \emph{technical report within 8 pages}, e.g. NIPS conference style 
\begin{center}
\url{https://nips.cc/Conferences/2016/PaperInformation/StyleFiles} 
\end{center}
or of a \emph{poster}, e.g. 
\begin{center}%\url{http://math.stanford.edu/~yuany/publications/poster_CleaveBioCPH2017_ForReview.pptx}
\url{https://github.com/yuany-pku/2017_math6380/blob/master/project1/DongLoXia_poster.pptx}
\end{center}
\subitem(b) \emph{ONE short presentation video within 10 mins}, e.g. in Youtube link. You may submit your presentation slides together with the video link to help understanding. 
\item In the report, (1) design or raise your scientific problems (a good problem is often more important than solving it); (2) show your main results with a careful analysis supporting the results toward answering your problems. Remember: scientific analysis and reasoning are more important than merely the performance results. Source codes may be submitted through email as a zip file, or as an appendix if it is not large.    
\item Submit your report by email or paper version no later than the deadline, to the following address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 2}. % (\href{mailto:datascience\_hw@126.com}{datascience\_hw@126.com}). 
\end{enumerate}

@@

\section*{Open Peer Review}

Deadline is 23:59 May 25, 2019. Submit your review in plain text to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 2 Review}. Rebuttal is open afterwards.

\begin{itemize}
\item Summary of the report.
\item Describe the strengths of the report. 
\item Describe the weaknesses of the report.
\item Evaluation on quality of writing (1-5): Is the report clearly written? Is there a good use of examples and figures? Is it well organized? Are there problems with style and grammar? Are there issues with typos, formatting, references, etc.? Please make suggestions to improve the clarity of the paper, and provide details of typos.
\item Evaluation on presentation (1-5): Is the presentation clear and well organized? Are the language flow fluent and persuasive? Are the slides clear and well elaborated? Please make suggestions to improve the presentation.
\item Evaluation on creativity (1-5): Does the work propose any genuinely new ideas? Is this a work that you are eager to read and cite? Does it contain some state-of-the-art results? As a reviewer you should try to assess whether the ideas are truly new and creative. Novel combinations, adaptations or extensions of existing ideas are also valuable.
\item Confidence on your assessment (1-3)
(3- I have carefully read the paper and checked the results, 2- I just browse the paper without checking the details, 1- My assessment can be wrong)
\end{itemize}

\section*{Rebuttal}
The rebuttal period starts from now, till 23:59 May 31, 2019. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in \emph{PLAIN TEXT} or \emph{Word Document} format to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 2 Rebuttal}.

\section{Crowdsourced Ranking Data on Allourideas}
The following datasets are crowdsourced pairwise ranking from platform Allourideas by Professor Mathew Salganik of Princeton Sociology. You may explore it with HodgeRank etc.

%\subsection{Pairwise Votings on Project 2 Reports}
%The following website hosts the crowdsourcing task on pairwise ranking on Project 2 reports:
%
%\url{http://www.allourideas.org/csic5011-project2}
%
%Up to Nov 26, 2017, the following dataset is collected at github:
%
%\url{https://github.com/yuany-pku/data/tree/master/allourideas/allourideas_csic5011-project2}
%
%\noindent where you may find 
%
%\begin{itemize}
%\item explanation of data file formats: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_csic5011-project2/allourideas%20-%20download%20your%20data.pdf}
%\item 12 reports as candidates: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_csic5011-project2/wikisurvey_report2_candidates_2017-11-26T07_20_24Z.csv}
%\item all valid votings: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_csic5011-project2/wikisurvey_report2_votes_2017-11-26T07_20_27Z.csv}
%\item all nonvotings: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_csic5011-project2/wikisurvey_report2_nonvotes_2017-11-26T07_20_30Z.csv} 
%\end{itemize}

\subsection{World College Rankings}
The following website hosts the crowdsourcing task on pairwise ranking on 270 universities in the world:

\url{http://www.allourideas.org/worldcollege}

Up to Nov 26, 2017, the following dataset is collected at github:

\url{https://github.com/yuany-pku/data/tree/master/allourideas/allourideas_worldcollege}

\noindent where you may find

\begin{itemize}
\item explanation of data file formats: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_worldcollege/allourideas%20-%20download%20your%20data.pdf}
\item 270 universities: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_worldcollege/wikisurvey_colleges_candidates_2017-11-26T07_14_53Z.csv}
\item all valid votings: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_worldcollege/wikisurvey_colleges_votes_2017-11-26T07_15_02Z.csv}
\item all nonvotings: \url{https://github.com/yuany-pku/data/blob/master/allourideas/allourideas_worldcollege/wikisurvey_colleges_nonvotes_2017-11-26T07_15_30Z.csv} 
\end{itemize}

This dataset has been used for various studies, e.g. Qianqian Xu, Jiechao Xiong, Xiaochun Cao, and Yuan Yao. False Discovery Rate Control and Statistical Quality Assessment of Annotators in Crowdsourced Ranking, ICML 2016, in \url{https://arxiv.org/abs/1605.05860v1}. An old dataset cleaned by Prof. Qianqian Xu from CAS can be found at

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/college.csv}

\subsection{Human Age Ranking}

The following dataset is kindly provided by Qianqian Xu, CAS, for the exploration on class.

The dataset is contained in the following zip file.

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/age.zip}

\noindent where you may find
\begin{enumerate}
\item \texttt{readme.txt}: description of data
\item \texttt{Agedata.mat}: data file collected
\item \texttt{Groundtruth.mat}: Groundtruth
\item \texttt{30 images.zip}: 30 human face images of different ages
\end{enumerate}

The basic problem is to rank the faces according to the ages, using all the information collected so far. A simple sub-problem is rank aggregation of ages from pairwise comparisons. If you are interested, you can try some generalized linear models (Qianqian Xu, Qingming Huang, Tingting Jiang, Bowei Yan, Weisi Lin, and Yuan Yao. HodgeRank on Random Graphs for Subjective Video Quality Assessment. IEEE Transactions on Multimedia, 14(3):844-857, 2012, \url{https://github.com/yao-lab/yao-lab.github.io/blob/master/reference/TMM12-final.pdf}) on this dataset, such as uniform model, Bradley-Terry model, Thurstone-Mosteller model, and Angular transform model. Compare maximum likelihood estimators and least square ones. The source code of this paper can be found at

\url{https://github.com/qianqianxu010/TMM2012}

A recent study with wider data is: Qianqian Xu, Jiechao Xiong, Xiaochun Cao, Qingming Huang, Yuan Yao, “From Social to Individuals: a Parsimonious Path of Multi-level Models for Crowdsourced Preference Aggregation”, IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI), 41(4):844-856, 2019, where the source codes can be downloaded at

\url{https://github.com/qianqianxu010/TPAMI2018}

\section{PageRank and Primary Eigenvectors}

The following dataset contains Chinese (mainland) University Weblink during 12/2001-1/2002,

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/univ_cn.mat}

\noindent where $\tt{rank\_{}cn}$ is the research ranking of universities in that year, $\tt{univ\_{}cn}$ contains the webpages of universities, and $\tt{W\_{}cn}$ is the link matrix whose $(i,j)-th$ element gives the number of links from university
$i$ to $j$.

\begin{enumerate}
\item Compute PageRank with Google's hyperparameter $\alpha=0.85$;
\item Compute HITS authority and hub ranking; 
\item Compare these rankings against the research ranking (you may consider Spearman's $\rho$ and Kendall's $\tau$ to compare different rankings);  
\item Compute extended PageRank with various hyperparameters $\alpha\in (0,1)$, investigate its effect on ranking. 
\end{enumerate}

For your reference, an implementation of PageRank and HITs can be found at

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/pagerank.m}

The following academic website link collects more countries with university links, for further explorations:

\url{http://cybermetrics.wlv.ac.uk/database/}

\section{Order the faces by Diffusion Map}
The following dataset contains 33 faces of the same person ($Y\in \R^{112\times 92\times33}$) in different angles,

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/face.mat}

You may create a data matrix $X\in \R^{n\times p}$ where $n=33,p=112\times92=10304$ \\ (e.g. {\texttt{X=reshape(Y,[10304,33])';}} in matlab).

\begin{enumerate}
\item Explore the Diffusion map, or the second smallest eigenvector of Markov Chains defined on the point cloud data, to order the faces, i.e., let $W_{ij}=\exp(-\|x_i - x_j\|^2/t)$ with $D=\diag(\sum_j W_{ij})$ and define $L=D^{-1} W - I$, clearly $\lambda_0=0$ and take the (second) smallest nonzero eigenvalue $\lambda_1$ with corresponding eigenvector $v_1$, sort the faces by values $v_1(i)$, $i=1,\ldots,n$.  
\item Explore the MDS-embedding of the 33 faces on top two eigenvectors: order the faces according to the top 1st eigenvector and visualize your results with figures. 
\item Explore the ISOMAP-embedding of the 33 faces on the $k=5$ nearest neighbor graph and compare it against the MDS results. Note: you may try Tenenbaum's Matlab code \\
{\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/isomapII.m}}
\item Explore the LLE-embedding of the 33 faces on the $k=5$ nearest neighbor graph and compare it against ISOMAP. Note: you may try the following Matlab code \\
{\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/lle.m}}
\end{enumerate}

You might explore larger datasets with other manifold learning methods, for example the PubFig dataset et al.

\url{http://www.cs.columbia.edu/CAVE/databases/pubfig/}

%{\em Nystr\"{o}m method:} In class, we have shown that every manifold learning algorithm can be regarded as Kernel PCA on graphs: (1) given $N$ data points, define a neighborhood graph with $N$ nodes for data points; (2) construct a positive semidefinite kernel $K$; (3) pursue spectral decomposition of $K$ to find the embedding (using top or bottom eigenvectors). However, this approach might suffer from the expensive computational cost in spectral decomposition of $K$ if $N$ is large and $K$ is non-sparse, e.g. ISOMAP and MDS. 
%
%To overcome this hurdle, Nystr\"{o}m method leads us to a scalable approach to compute eigenvectors of low rank matrices.  
%Suppose that an $N$-by-$N$ positive semidefinite matrix $K\succeq 0$ admits the following block partition
%\begin{equation}
%K = \left[
%\begin{array}{cc}
%A & B \\
%B^T & C
%\end{array}
%\right].
%\end{equation}
%where $A$ is an $n$-by-$n$ block. Assume that $A$ has the spectral decomposition $A=U \Lambda U^T$, $\Lambda=\diag(\lambda_i)$ ($\lambda_1\geq \lambda_2 \geq \ldots \lambda_k > \lambda_{k+1}=\ldots=0$) and $U=[u_1,\ldots,u_n]$ satisfies $U^TU=I$. 
%\begin{enumerate}
%\item Assume that $K=X X^T$ for some $X=[X_1; X_2] \in \R^{N\times k}$ with the block $X_1\in \R^{n\times k}$. Show that $X_1$ and $X_2$ can be decided by:
%\begin{equation}\label{eq:x1}
% X_1 = U_k \Lambda_k^{1/2}, 
%\end{equation}
%\begin{equation} \label{eq:x2}
%X_2 = B^T U_k \Lambda_k^{-1/2}, 
%\end{equation}
%%\[ X_1 X_1^T = A \Rightarrow X_1 = U_k \Lambda_k^{1/2}, \]
%%\[ X_1 X_2^T = B \Rightarrow X_2 = B^T U_k \Lambda_k^{-1/2}. \]  
%where $U_k=[u_1, \ldots, u_k]$ consists of those $k$ columns of $U$ corresponding to top $k$ eigenvalues $\lambda_i$ ($i=1,\ldots,k$).  
%\item Show that for general $K\succeq 0$, one can construct an approximation from \eqref{eq:x1} and \eqref{eq:x2}, 
%\begin{equation}
%\hat{K} = \left[
%\begin{array}{cc}
%A & B \\
%B^T & \hat{C} 
%\end{array}
%\right].
%\end{equation}
%where $A=X_1 X_1^T$, $B= X_1 X_2^T$, and $\hat{C}=X_2 X_2^T =   B^T A^\dagger B$, $A^\dagger$ denoting the Moore-Penrose (pseudo-) inverse of $A$. Therefore $\|\hat{K}-K\|_F =\|C- B^T A^\dagger B\|_F$. Here the matrix $C-B^T A^\dagger B=:K/A$ is called the (generalized) \emph{Schur Complement} of $A$ in $K$.
%\item Explore Nystr\"{o}m method on the Swiss-Roll dataset (\url{http://www.math.pku.edu.cn/teachers/yaoy/data/swiss_roll_data.mat} contains 3D-data X) with ISOMAP. To construct the block $A$, you may choose either of the following: 
%\subitem $n$ random data points; 
%\subitem *$n$ landmarks as minimax $k$-centers (\url{http://www.math.pku.edu.cn/teachers/yaoy/Spring2011/matlab/kcenter.m}); \\
%Some references can be found at: 
%\subitem[dVT04] Vin de Silva and J. B. Tenenbaum, ``Sparse multidimensional scaling using landmark points", 2004, downloadable at \url{http://pages.pomona.edu/~vds04747/public/papers/landmarks.pdf};  
%\subitem[P05] John C. Platt, ``FastMap, MetricMap, and Landmark MDS are all Nystr\"{o}m Algorithms", 2005, downloadable at \url{http://research.microsoft.com/en-us/um/people/jplatt/nystrom2.pdf}. 
%\item *Assume that $A$ is invertible, show that  
%\[ \det(K) = \det(A)\cdot \det(K/A), \]
%\item *Assume that $A$ is invertible, show that 
%\[ \rank(K)=\rank(A)+\rank(K/A). \]
%\item *Can you extend the identities in (c) and (d) to the case of noninvertible $A$? A good reference can be found at, 
%\subitem[Q81] Diane V. Quellette, ``Schur Complements and Statistics", Linear Algebra and Its Applications, 36:187-295, 1981. \url{http://www.sciencedirect.com/science/article/pii/0024379581902329}
%\end{enumerate}

\section{Transition Paths of Karate Club Network} 
The following dataset contains a 34-by-34 adjacency matrix $A$ of Zachery's Karate Club Network.

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/karate.mat}

As shown in Figure \ref{fig:karate}, node 1 represents the coach of the club and node 34 is the owner (president) of the club. The undirected, unweighted edges between nodes represent
the affinity relation between club members. The story behind the network is this: the coach would like to raise the instruction fee while the president does not allow this; the conflicts finally result in a fission of the club -- the coach leaves the club with his funs and sets up his own club marked in red, and the blue nodes remain in the old club with the president.  
\begin{figure}[h]
\centering
\includegraphics[width=0.3\textwidth]{./figures/karate1-a_old.eps}
\caption{Zachery's Karate Club Network}\label{fig:karate}
\end{figure}

A. Apply the spectral clustering via the Cheeger vector (the second smallest eigenvector associated with normalized Graph Laplacian) to bipartite the network into two components, and compare it with the ground truth fission above.

B. Perform the following experiment with the transition path analysis. 
\begin{enumerate}
\item Define a Markov chain according to the network structure, such that from each node a random walker will jump to its neighbors with equal probability, i.e. $P=D^{-1} A$ where $D=\diag(d_i)$ and $d_i = \sum_j A_{ij}$;
\item Compute its stationary distribution $\pi(i)\sim d_i$. 
\item Define the source set $V_0=\{1\}$ and the target set $V_1=\{34\}$, compute the committor function
\[  q(x) = Prob(\mbox{trajectory starting from $x$ hitting $V_1$ before $V_0$}) \]
by solving the following Dirichlet boundary problem
\[ (L q)(x) = 0, \ \ \ x\in V_u := V -\{1,34\}, \ \ \ q(1)=0,\ q(34)=1. \]
Find those edges which contains one node $q(x)\leq 0.5$ and the other node $q(x)\geq 0.5$. Such edge set defines a cut of the graph. 
\item Compute the effective flux on each edge $(x,y)$ by 
\[ J^+(x,y) = \max(J(x,y) - J(y,x), 0 ),\]
where
\[     J(x,y) = 
     \begin{cases}
       \pi(x) (1-q(x)) P_{xy}q(y), & x\neq y;\\
       0, & \text{otherwise}.
     \end{cases}
\]
\item Compute the transition flux through each node $x\in V$ by 
\[
     T(x) = \left\{\begin{array}{ll}
     \sum_{y \in V} J^+(x,y) ,& x\in V_0 \\
     \sum_{y\in V} J^+(y,x), & x\in V_1 \\
     \sum_{y\in V} J^+(x,y) = \sum_{y\in V} J^+(y,x), & x\in V_u 
     \end{array}\right.
\]
\item Visualize your results by plotting a directed graph, with an arrow on each edge indicating the effective flux direction $J^+(x,y)>0$, different color marking the cut set of the graph, and if possible edge/node size in proportion to the size of effective/transition flux.
\end{enumerate}

A reference can be seen at:
\begin{itemize}
\item Weinan E, Jianfeng Lu, and Yuan Yao. {\it The Landscape of Complex Networks: Critical Nodes and A Hierarchical Decomposition}. Methods and Applications of Analysis, special issue in honor of Professor Stanley Osher on his 70th birthday, 20(4):383-404, 2013. \\ arXiv: \url{http://arxiv.org/abs/1204.6376}. \\
Pdf Link: \url{https://github.com/yao-lab/yao-lab.github.io/blob/master/reference/ELY.MAA13.pdf} 
\end{itemize}

The following matlab codes implement the transition path analysis and reproduce the results in the paper above:

\url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/karate_tpt.m}

You may explore more networks, including the two other examples in the paper above:

LAO-binding network (provided by Xuhui Huang): \url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/lao54.mat}

Les Miserables social network: \url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/lesmis.mat}, or \url{https://github.com/yao-lab/yao-lab.github.io/blob/master/data/lesmis.txt}

\section{Identification of Raphael's paintings from the forgeries}

The following data, provided by Prof. Yang WANG from HKUST,

\url{https://drive.google.com/folderview?id=0B-yDtwSjhaSCZ2FqN3AxQ3NJNTA&usp=sharing}

\noindent contains a 28 digital paintings of Raphael or forgeries. Note that there are both jpeg and tiff files, so be careful with the bit depth in digitization. The following file

\url{https://docs.google.com/document/d/1tMaaSIrYwNFZZ2cEJdx1DfFscIfERd5Dp2U7K1ekjTI/edit}

\noindent contains the labels of such paintings, which are 
\begin{enumerate}
\item[1] Maybe Raphael - Disputed
\item[2] Raphael
\item[3] Raphael
\item[4] Raphael
\item[5] Raphael
\item[6] Raphael
\item[7] Maybe Raphael - Disputed
\item[8] Raphael
\item[9] Raphael
\item[10] Maybe Raphael - Disputed
\item[11] Not Raphael
\item[12] Not Raphael
\item[13] Not Raphael
\item[14] Not Raphael
\item[15] Not Raphael
\item[16] Not Raphael
\item[17] Not Raphael
\item[18] Not Raphael
\item[19] Not Raphael
\item[20] My Drawing (Raphael?)
\item[21] Raphael
\item[22] Raphael
\item[23] Maybe Raphael - Disputed
\item[24] Raphael
\item[25] Maybe Raphael - Disputed
\item[26] Maybe Raphael - Disputed
\item[27] Raphael
\item[28] Raphael
\end{enumerate}
Can you exploit the known Raphael vs. Not Raphael data to predict the identity of those 6 disputed paintings (maybe Raphael)? The following student poster report seems a good exploration

\url{https://yao-lab.github.io/2015.fall.pku/poster/Raphael_LI%2CYue_1300010601.pdf}

The following paper by Haixia Liu, Raymond Chan, and me studies Van Gogh's paintings which might be a reference for you:

\url{http://dx.doi.org/10.1016/j.acha.2015.11.005}

\section*{Datasets from Project 1}

{\it All the following datasets have been given in project 1. But you may explore these data with various new techniques learned in class, e.g. Robust PCA, Sparse PCA, Robust PCA by GAN (\url{https://github.com/zhuwzh/Robust-GAN-Scatter}), Manifold Learning, Topological Data Analysis (Mapper, Persistent Homology, etc.). }

@@

@@
